Astrophysical calibration of gravitational-wave detectors

### 2015-09-30 docs/cosmic_cal.tex
Minor changes

\author{L.~Wright}\affiliation{SUPA, School of Physics and Astronomy, University of
  Glasgow, Glasgow G12 8QQ, United Kingdom}
\author{M.~Pitkin}\affiliation{SUPA, School of Physics and Astronomy, University of
  Glasgow, Glasgow G12 8QQ, United Kingdom}
\author{C.~Messenger}\affiliation{SUPA, School of Physics and Astronomy, University of
  Glasgow, Glasgow G12 8QQ, United Kingdom}

\email{matthew.pitkin@glasgow.ac.uk}
\email{christopher.messenger@glasgow.ac.uk}

@@

% BNS systems are GRBs
It is considered likely that the merger of \ac{BNS} systems, in addition to emitting detectable 
\acp{GW}, is also the mechanism for producing \acp{sGRB}. In this scenario these \ac{EM} events are 
produced through the ... and result in tightly beamed emission parallel to the orbital angular 
momentum vector of the \ac{BNS} system. Additional evidence for the coincidence of \acp{sGRB} with
\ac{GW} events are the estimated astrophysical rates of both phenomena. Observations of \acp{sGRB} 
give a rate of XXX Mpc$^{-3}$yr$^{-1}$ which can be compared to estimates of \ac{BNS} merger rates 
of XXX-XXX Mpc$^{-3}$yr$^{-1}$. This latter range is obtained from population synthesis models 
together with knowledge of the X known \ac{BNS} systems in our galaxy.

@@

\begin{figure*}
 \begin{center}
  \includegraphics[width=1.0\textwidth]{bns_post_fig.pdf}
 \end{center}
 \caption{\label{fig:bnspost} The marginalised posterior probability distributions for the unknown
 parameters of a \ac{BNS} system, including calibration scaling factors for the three detectors 
(H1, L1 and V1). The injected signal was at a distance of 250\,Mpc, had \ac{SNR} of 8.7, 10.9 and 
4.1 and percentage uncertainties in the calibration scale factors of 14\%, 11\% and 27\% for each 
of the detectors respectively.~\cm{The fonts are a bit small.  Maybe also
highlight somehow the boxes refereing to the scale factors?}}
\end{figure*}

\begin{figure*}
 \begin{center}
  \includegraphics[width=1.0\textwidth]{nsbh_post_fig.pdf}
 \end{center}
 \caption{\label{fig:nsbhpost} The marginalised posterior probability distributions for the unknown
 parameters of a \ac{NSBH} system, including calibration scaling factors for the three detectors 
(H1, L1 and V1). The injected signal was at a distance of 450\,Mpc, had \ac{SNR} of 7.7, 10.9 and 
4.2 and percentage uncertainties in the calibration scale factors of 17\%, 14\% and 34\% for each of 
the detectors respectively.~\cm{same things about the fonts and highlighting
the scale factors.}}
\end{figure*}

>>>>

\author{M.~Pitkin}
\email{matthew.pitkin@glasgow.ac.uk}
\affiliation{SUPA, School of Physics and Astronomy, University of
  Glasgow, Glasgow G12 8QQ, United Kingdom}
\author{C.~Messenger}
\email{christopher.messenger@glasgow.ac.uk}
\affiliation{SUPA, School of Physics and Astronomy, University of
  Glasgow, Glasgow G12 8QQ, United Kingdom}
\author{L.~Wright}
\altaffiliation{Now at: School of Mathematics and Physics, Queen's University Belfast, Belfast BT7 
1NN, United Kingdom}
\affiliation{SUPA, School of Physics and Astronomy, University of
  Glasgow, Glasgow G12 8QQ, United Kingdom}

@@

% BNS systems are GRBs
It is considered likely that the merger of \ac{BNS} and/or \ac{NSBH} systems, in addition to 
emitting detectable \acp{GW}, is also the mechanism for producing \acp{sGRB} 
\cite{1992ApJ...395L..83N}. In this scenario these events produce tightly beamed \ac{EM} emission 
parallel to the orbital angular 
momentum vector of the \ac{BNS} system. Additional evidence for the coincidence of \acp{sGRB} with
\ac{GW} events are the estimated astrophysical rates of both phenomena. Observations of \acp{sGRB} 
give a rate of XXX Mpc$^{-3}$yr$^{-1}$ which can be compared to estimates of \ac{BNS} merger rates 
of XXX-XXX Mpc$^{-3}$yr$^{-1}$, or \ac{NSBH} merger rates. The ranges of rates for \acp{BNS} 
is obtained from population synthesis models together with knowledge of the X known \ac{BNS} systems 
in our galaxy, whilst the range for \acp{NSBH} is entirely from population synthesis as not such 
systems have been observed.

@@

\begin{figure*}
 \begin{center}
  \includegraphics[width=1.0\textwidth]{bns_post_fig.pdf}
 \end{center}
 \caption{\label{fig:bnspost} The marginalised posterior probability distributions for the unknown
 parameters of a \ac{BNS} system, including calibration scaling factors (surrounded by the red 
borders) for the three detectors (H1, L1 and V1). The injected signal was at a distance of 
250\,Mpc, had \ac{SNR} of 8.7, 10.9 and 4.1 and percentage uncertainties in the calibration scale 
factors of 14\%, 11\% and 27\% for each of the detectors respectively.}
\end{figure*}

\begin{figure*}
 \begin{center}
  \includegraphics[width=1.0\textwidth]{nsbh_post_fig.pdf}
 \end{center}
 \caption{\label{fig:nsbhpost} The marginalised posterior probability distributions for the unknown
 parameters of a \ac{NSBH} system, including calibration scaling factors for the three detectors 
(H1, L1 and V1). The injected signal was at a distance of 450\,Mpc, had \ac{SNR} of 7.7, 10.9 and 
4.2 and percentage uncertainties in the calibration scale factors of 17\%, 14\% and 34\% for each of 
the detectors respectively.}
\end{figure*}
